Modular Curves

### 2020-01-24 paper.tex
moduli spaces

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
%\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

From now on we will often say complex elliptic curve, instead of complex torus to highlight their interpretation as elliptic curves. Further, we will often denote complex elliptic curves with a simple symbold (often $E$) instead of always writing them as the quotient  $\C / \Lambda$.

@@

\section{Modular Curves and Moduli Spaces} \label{sec:modular_curves_and_moduli_spaces}
The title of this paper is modular curves, but so far have not defined these. 
The definition of these objects is very simple, but like any object in this paper, the real suprises are it's relations to other objects. 
\begin{definition}
	Let $\Gamma \subset \SL_2\Z$ be any congruence subgroup. Then the \emph{modular curve} $Y(\Gamma)$ is defined as the set of orbits of $\mathcal{H} $ under  $\Gamma$, \[
		Y(\Gamma) = \mathcal{H} / \sim = \{\Gamma \tau \;|\; \tau \in \mathcal{H} \} 
	.\] 
\end{definition}
Re call the subgroups $\Gamma(N), \Gamma_1(N), \Gamma_0(N)$ from \cref{sec:subgroups_of_the_modular_group}. 
Often we are interested in the modular curves corresponding to these congruence subgroups, so we denote \[
	Y_0(N) = Y(\Gamma(N)),\; Y_1(N) = Y(\Gamma_1(N)),\; Y(N) = Y(\Gamma(N))
.\]

@@

\subsection{Enhanced Elliptic Curves and Moduli Spaces} \label{sec:enhanced_elliptic_curves_and_moduli_spaces}
There are three common ways of `adding information' to elliptic curves, creating \emph{enhanced elliptic curves}. Moduli Spaces are equivalence classes of enhanced elliptic curves.  
\begin{definition} \hspace{\linewidth}
	\begin{enumerate}
		\item An \emph{enhanced elliptic curve for $\Gamma_0(N)$} is an pair $(E, C)$ where  $E$ is a complex elliptic curve and $C$ is an cyclic subgroup of order $N$.
		Two of these curves $(E_1, C_1), (E_2, C_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that restricts to an isomorphism from $C_1$ to $C_2$.
		The associated \emph{moduli space} is \[
			S_0(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma_1(N)$} is an pair $(E, Q)$ where  $E$ is a complex elliptic curve and $Q$ is point in $E$ of order $N$.
		Two of these curves $(E_1, Q_1), (E_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $Q_1$ to $Q_2$.
		The associated \emph{moduli space} is \[
			S_1(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma(N)$} is an tripple $(E, P, Q)$ where  $E$ is a complex elliptic curve and $P, Q$ are points in the $N$-torsion subgroup $E[N]$ such  that the weil pairing  $e_N(P, Q) = 1$.
		Two of these curves $(E_1, P_1, Q_1), (E_2, P_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $P_1$ to $P_2$ and $Q_1$ to $Q_2$
		The associated \emph{moduli space} is \[
			S(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\end{enumerate}	
\end{definition}
\Cref{fig:enhanced_elliptic_curves} gives a visualisation of these enhanced elliptic curves.
\begin{figure}[h]
	\centering
	\incfig{enhanced_elliptic_curves}
	\caption{Enhanced elliptic curves}
	\label{fig:enhanced_elliptic_curves}
\end{figure}
The following theorem gives a generalisation of the conclusion of \cref{sec:modular_curves_and_moduli_spaces}, showing that there are bijections in the modular curves $Y_0(N), Y_1(N), Y(N)$ and the moduli spaces $S_0(N), S_1(N), S(N)$, as well as providing more insight in what the moduli spaces look like. 
\begin{theorem}
	\hspace{\linewidth}
	\begin{enumerate}
		\item Every enhanced elliptic curve for $\Gamma_0(N)$ is equivalent to $(E_\tau, \left<1 / N + \Lambda_\tau \right>$ 
	\end{enumerate}
\end{theorem}

@@

The Weierstrass function $\wp_{\Lambda}$ has only one pole of order 2. Hence in this case  $n = 2$.
\item 
	We will show this by first calculating \[
		\frac{1}{2\pi i}\int_{\partial P + t} z \frac{f(z)}{f'(z)} \mathrm d z
	\]
	and showing that this value must be in $\Lambda$.
	Like in the first part of this exercise we will split up the boundary in its edges.
	\[	
		\int_{\partial P+ t} z \frac{f(z)}{f'(z)} \mathrm d z = \left(\int_t^{\omega_2 + t} + \int_{\omega_2+t}^{\omega_1 + \omega_2 + t} + \int_{\omega_1 + \omega_2 + t} ^{\omega_1 + t} + \int_{\omega_1}^{t}\right) z \frac{f(z)}{f'(z)} \mathrm dz
	.\]
	By $\Lambda$-periodicity we know that the factor $f(z) / f'(z)$ is the same on opposing edges. Hence we can write \begin{align*}
		\int_{\partial P + t} z \frac{f(z)}{f'(z)} \mathrm d z &= \int_t^{\omega_1 + t} (z + \omega_2 - z) \frac{f(z)}{f'(z)} \mathrm d z + \int_{t}^{\omega_2 + t} (z - z - \omega_1) \frac{f(z)}{f'(z)} \mathrm d z\\
								       &= \omega_2 \int_t^{\omega_1 + t} 1 \; \mathrm d \ln f(z) - \omega_1 \int_t^{\omega_2 +t} 1 \; \mathrm d \ln f(z) \\
	.\end{align*} 
	From this we see that the integrals must be integer multiples of  $2\pi i$. 
	Hence 
	\[
		\frac{1}{2\pi i } \int_{\partial P + t} z \frac{f(z)}{f'(z)} \mathrm d z \in \Lambda
	.\] 
	Now note that we can write $f(z) = \sum_{x \in \{\text{poles or zero}\} }(z - x)^{\nu_x(f)}g(z)$ for some some simple function $g$. 
	So \[
		\frac{zf'(z)}{f(z)} = \sum_{x \in \{\text{poles or zero}\} }\nu_x(f) \frac{z}{ z - x} + z \frac{g'(z)}{g(z)}
	.\] 
	Note that this function has poles with residue $x \nu_x(f)$ for every $x$ which is a pole or zero of  $f$. By the residue theorem  \[
		\frac{1}{2\pi i} \int_{\partial P + t} z \frac{f'(z)}{f(z)} \mathrm d z = \sum_{x \in \C / \Lambda} \nu_x(f)  x \in \Lambda 
	.\]  
\end{enumerate}
\end{proof}
\printbibliography
\end{document}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{color}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

From now on we will often say complex elliptic curve, instead of complex torus to highlight their interpretation as elliptic curves. Further, we will often denote complex elliptic curves with a simple symbold (often $E$) instead of always writing them as the quotient  $\C / \Lambda$. We write $E_\tau  = \C / \Lambda_\tau$.

@@

\section{Modular Curves and Moduli Spaces} \label{sec:modular_curves_and_moduli_spaces}
The title of this paper is modular curves, but so far have not defined these. 
The definition of these objects is very simple, but like any object in this paper, the real suprises are it's relations to other objects. 
\begin{definition}
	Let $\Gamma \subset \SL_2\Z$ be any congruence subgroup. Then the \emph{modular curve} $Y(\Gamma)$ is defined as the set of orbits of $\mathcal{H} $ under  $\Gamma$, \[
		Y(\Gamma) = \mathcal{H} / \sim = \{\Gamma \tau \;|\; \tau \in \mathcal{H} \} 
	.\] 
\end{definition}
Recall the subgroups $\Gamma(N), \Gamma_1(N), \Gamma_0(N)$ from \cref{sec:subgroups_of_the_modular_group}. 
Often we are interested in the modular curves corresponding to these congruence subgroups, so we denote \[
	Y_0(N) = Y(\Gamma(N)),\; Y_1(N) = Y(\Gamma_1(N)),\; Y(N) = Y(\Gamma(N))
.\]

@@

\subsection{Enhanced Elliptic Curves and Moduli Spaces} \label{sec:enhanced_elliptic_curves_and_moduli_spaces}
There are three common ways of `adding information' to elliptic curves, creating \emph{enhanced elliptic curves}. Moduli Spaces are equivalence classes of enhanced elliptic curves.  
\begin{definition} \hspace{\linewidth}
	\begin{enumerate}
		\item An \emph{enhanced elliptic curve for $\Gamma_0(N)$} is an pair $(E, C)$ where  $E$ is a complex elliptic curve and $C$ is an cyclic subgroup of order $N$.
		Two of these curves $(E_1, C_1), (E_2, C_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that restricts to an isomorphism from $C_1$ to $C_2$.
		The associated \emph{moduli space} is \[
			S_0(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma_1(N)$} is an pair $(E, Q)$ where  $E$ is a complex elliptic curve and $Q$ is point in $E$ of order $N$.
		Two of these curves $(E_1, Q_1), (E_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $Q_1$ to $Q_2$.
		The associated \emph{moduli space} is \[
			S_1(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma(N)$} is an tripple $(E, P, Q)$ where  $E$ is a complex elliptic curve and $P, Q$ are points in the $N$-torsion subgroup $E[N]$ such  that the weil pairing  $e_N(P, Q) = 1$.
		Two of these curves $(E_1, P_1, Q_1), (E_2, P_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $P_1$ to $P_2$ and $Q_1$ to $Q_2$
		The associated \emph{moduli space} is \[
			S(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\end{enumerate}	
\end{definition}
\begin{figure}[h]
	\centering
	\incfig{enhanced_elliptic_curves}
	\caption{Enhanced elliptic curves}
	\label{fig:enhanced_elliptic_curves}
\end{figure}
\Cref{fig:enhanced_elliptic_curves} gives a visualisation of these enhanced elliptic curves.
The following theorem gives a generalisation of the conclusion of \cref{sec:modular_curves_and_moduli_spaces}, showing that there are bijections in the modular curves $Y_0(N), Y_1(N), Y(N)$ and the moduli spaces $S_0(N), S_1(N), S(N)$, as well as providing more insight in what the moduli spaces look like. 
\begin{theorem}
	\hspace{\linewidth}
	\begin{enumerate}
		\item Every enhanced elliptic curve for $\Gamma_0(N)$ is equivalent to curve of the form $(E_\tau, \left<1 / N + \Lambda_\tau \right>)$ for some $\tau \in \mathcal{H} $. 
			Two curves in this form $(E_\tau, \left<1 / N + \Lambda_\tau \right>)$ and $(E_\sigma, \left<1 / N + \Lambda_\sigma \right>)$ are equivalent if and only if $\Gamma_0\left( N \right) \tau = \Gamma_0(N) \sigma$. There is a bijective correspondence
			\begin{align*}
				S_0(N) &\longrightarrow Y_0(N) \\
				\left[\frac{\C}{\Lambda_\tau}, \left<\frac{1}{N} + \Lambda_\tau \right>\right] &\longmapsto \Gamma_0(\N)\tau
			.\end{align*}

		\item Every enhanced elliptic curve for $\Gamma_1(N)$ is equivalent to curve of the form $(E_\tau, 1 / N + \Lambda_\tau )$ for some $\tau \in \mathcal{H} $. 
			Two curves in this form $(E_\tau, 1 / N + \Lambda_\tau )$ and $(E_\sigma, 1 / N + \Lambda_\sigma)$ are equivalent if and only if $\Gamma_1\left( N \right) \tau = \Gamma_1(N) \sigma$. There is a bijective correspondence
			\begin{align*}
				S_1(N) &\longrightarrow Y_1(N) \\
				\left[\frac{\C}{\Lambda_\tau}, \frac{1}{N} + \Lambda_\tau \right] &\longmapsto \Gamma_1(\N)\tau
			.\end{align*}
		\item Every enhanced elliptic curve for $\Gamma(N)$ is equivalent to curve of the form $(E_\tau, \tau / N + \Lambda_\tau, 1 / N + \Lambda_\tau )$ for some $\tau \in \mathcal{H} $. 
			Two curves in this form $(E_\tau, \tau / N + \Lambda_\tau,  1 / N + \Lambda_\tau )$ and $(E_\sigma, \sigma / N + \Lambda_\sigma,1 / N + \Lambda_\sigma)$ are equivalent if and only if $\Gamma\left( N \right) \tau = \Gamma(N) \sigma$. There is a bijective correspondence
			\begin{align*}
				S(N) &\longrightarrow Y(N) \\
				\left[\frac{\C}{\Lambda_\tau}, \frac{\tau}{N} + \Lambda_\tau, \frac{1}{N} + \Lambda_\tau \right] &\longmapsto \Gamma_1(\N)\tau
			.\end{align*}
	\end{enumerate}
\end{theorem}
\begin{proof}
	\begin{enumerate}
		\item Let $\left( C / \Lambda, \left< c \omega_1 / N  + d \omega_2 / N  + \Lambda\right> \right) $, where $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ be any enhanced complex elliptic curve for $\Gamma_0(N)$.
			As $c \omega_1 / N + d \omega_2 /N$ generates a cyclic group of order $N$ we know that $\gcd(c, d, N) = 1$. 
			So there exists an $x \in \Z$ such that $\gcd(c, d + xN) = 1$. 
			Note that \[
				c \frac{\omega_1}{N}  + d \frac{\omega_2}{N}  + \Lambda =  c \frac{\omega_1}{N} + (d + xN) \frac{\omega_2}{N}+ \Lambda
		.\]
		We may as well have assumed from the start that $c, d$ are coprime.
		So there are $a, b \in \Z $ such that $ac - bd = 1$. 
		This means that the matrix  $\begin{pmatrix} a & b \\ c& d \end{pmatrix}  \in \SL_2\Z$ and hence invertible. 
		Let \[
		\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
		\begin{pmatrix} a & b \\ c & d \end{pmatrix} 
		\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
		.\] 
		As this is an invertible matrix it follows that $\Lambda = \omega_1' \Z \oplus \omega_2' \Z$. 
	In this new basis we see that the enhanced elliptic curve looks like $(\C / \Lambda, \left< 1 / N \omega_2\right>)$.
	Recall from \cref{sec:modular_forms_and_complex_tori} that  $\phi: z  + \Lambda \mapsto  \frac{1}{\omega_2'} z + \Lambda_\tau$ with $\tau = \frac{\omega_1}{\omega_2}$. 
	This maps  $\left<\omega_2 / N \right>$ to $\left<1 / N + \Lambda_\tau \right>$.
	Hence  \[
		\left( \frac{\C}{\Lambda}, \left<c \frac{\omega_1}{N} + d \frac{\omega_2}{N} \right> \right) 	\simeq  
		\left( E_\tau, \left<\frac{1}{N} + \Lambda_\tau \right> \right) 
	.\]

	We will know prove that \[
		\left( E_\tau , \left<\frac{1}{N} + \Lambda_\tau \right> \right) \simeq 
		\left( E_\sigma, \left<\frac{1}{N} + \Lambda_\sigma \right> \right) 
	\]
	if and only if $\tau = \gamma \cdot \sigma$ for some $\gamma \in \Gamma_0(N)$.
	Recall that $\Gamma_0(N)$ is the set of all matrices $\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ where $c$ is divisible by $N$. 
	\ltr Suppose that $\phi: z \mapsto m z$ is such an isomorphism. Then $m \Lambda_\tau = \Lambda_\sigma$. Hence \[
	\begin{pmatrix} m \tau \\ m \end{pmatrix}  = 
	\begin{pmatrix} a & b \\ c & d \end{pmatrix} \begin{pmatrix} \sigma \\ 1 \end{pmatrix} 
	,\] 
	for some $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix}  \in \SL_2\Z$. 
	We see that $\tau = \gamma \sigma$. If we can show that  $N \mathbin{\mid} c$ we are done.
	We know that $m = c \sigma + d$. 
	We know that $\phi$ maps $1 / N + \Lambda_\tau$ to a generator of $\left<1 / N + \Lambda_\sigma \right>$. 
	Putting this together yields \begin{align*}
		m\left(\frac{1}{N} + \Lambda_\tau\right) &= (c \tau + d) \frac{1}{N} + \Lambda_\sigma \\ 
		&= c \frac{\sigma}{N} + d \frac{1}{N} + \Lambda_\sigma \\
	\end{align*}
	So we see that $N \mathbin{|} c$. 
	\rtl Suppose that $\tau = \gamma \cdot \sigma$ for some \[
		\gamma = \begin{pmatrix} a & b \\ c & d  \end{pmatrix} \in \Gamma_0(N)
	.\] 
	Define  $m = c \sigma + d$. Reversing the reasoning for the other implication yields that  $\phi: z\mapsto  m z$ is an isomorphism.

	\item The first part is completely analogous to the case for $\Gamma_0.$ 
	We will know prove that \[
		\left( E_\tau , \frac{1}{N} + \Lambda_\tau \right) \simeq 
		\left( E_\sigma, \frac{1}{N} + \Lambda_\sigma \right) 
	\]
	if and only if $\tau = \gamma \cdot \sigma$ for some $\gamma \in \Gamma_1(N)$.
	Recall that $\Gamma_0(N)$ is the set of all matrices $\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ where $c \equiv 0, a \equiv d \equiv 1 \mod N$.

	\ltr Suppose that $\phi: z\mapsto  m z$ is such an isomorphism is such an isomorphism.
	Then $m \Lambda_\tau = \Lambda_\sigma$ for some $m$. So \[
	\begin{pmatrix} m \tau \\ m \end{pmatrix} = 
	\gamma \cdot  \begin{pmatrix} \sigma \\ 1 \end{pmatrix} , 
	\text{ for some } \gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2 \Z
	.\] 
	Then $m = c \sigma + d$. So 
	 \begin{align*}
		 m \left( \frac{1}{N} + \Lambda_\tau \right)  &= c \frac{\sigma}{N} + d \frac{1}{N} + \Lambda_\sigma \\
		 &=  \frac{1}{N} + \Lambda_\sigma
	.\end{align*}
	From this we see that $c \equiv 0, d \equiv 1 \mod N$. Recall that  $ad - bc = 1$. 
	So  $ad - bc \equiv a\cdot 1 + b\cdot 0 \equiv a \equiv 1$. So $\gamma \in \Gamma_1(N)$.
	\rtl Suppose that $\tau = \gamma \cdot \sigma$ for some \[
		\gamma = \begin{pmatrix} a & b \\ c & d  \end{pmatrix} \in \Gamma_1(N)
	.\] 	
	Define $m = c \sigma + d$. Reversing the argument for the other implication yields that $\phi:z \mapsto m z$ is an isomorphism.

	\item Let 
		\[\left( C / \Lambda, a \frac{\omega_1}{N} + b \frac{\omega_2}{N} + \Lambda,  c \frac{\omega_1}{N}  + d \frac{\omega_2}{N}  + \Lambda \right) ,\]
	where $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ be any enhanced complex elliptic curve for $\Gamma(N)$.
	As the Weil pairing of the two points is 1 we know that $ad - bc \equiv 1 \mod N $. 
	It can be shown that we can find $a', b', c', d' \equiv a, b, c, d \mod N$ such that  $a'd' - b'c' = 1$. 
	We will assume that this has been the case from the beginning. 
	This means that the matrix  $\begin{pmatrix} a & b \\ c& d \end{pmatrix}  \in \SL_2\Z$ and hence invertible. 
	Let \[
		\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
		\begin{pmatrix} a & b \\ c & d \end{pmatrix} 
		\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\] 
	As this is an invertible matrix it follows that $\Lambda = \omega_1' \Z \oplus \omega_2' \Z$. 
	In this new basis we see that the enhanced elliptic curve looks like $(\C / \Lambda, 1 / N \omega_1,  1 / N \omega_2)$.
	Recall from \cref{sec:modular_forms_and_complex_tori} that  $\phi: z  + \Lambda \mapsto  \frac{1}{\omega_2'} z + \Lambda_\tau$ with $\tau = \frac{\omega_1}{\omega_2}$. 
	This maps  $\left<\omega_2 / N \right>$ to $\left<1 / N + \Lambda_\tau \right>$.
	Hence  \[
		\left( C / \Lambda, a \frac{\omega_1}{N} + b \frac{\omega_2}{N} + \Lambda,  c \frac{\omega_1}{N}  + d \frac{\omega_2}{N}  + \Lambda \right)
		\simeq
		\left( E_\tau, \frac{\tau}{N} + \Lambda_\tau, \frac{1}{N} + \Lambda_\tau \right)
	.\]

	We will know prove that \[
		\left( E_\tau , \frac{\tau}{N} + \Lambda_\tau, \frac{1}{N} + \Lambda_\tau \right) \simeq 
		\left( E_\sigma, \frac{\sigma}{N} + \Lambda_ \sigma, \frac{1}{N} + \Lambda_\sigma \right) 
	\]
	if and only if $\tau = \gamma \cdot \sigma$ for some $\gamma \in \Gamma(N)$.
	Recall that $\Gamma_0(N)$ is the set of all matrices $\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ where $c \equiv d \equiv 0, a \equiv d \equiv 1 \mod N$.

	\ltr Suppose that $\phi: z\mapsto  m z$ is such an isomorphism is such an isomorphism.
	Then $m \Lambda_\tau = \Lambda_\sigma$ for some $m$. So \[
	\begin{pmatrix} m \tau \\ m \end{pmatrix} = 
	\gamma \cdot  \begin{pmatrix} \sigma \\ 1 \end{pmatrix} , 
	\text{ for some } \gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2 \Z
	.\] 
	Then $m = c \sigma + d$. So 
	 \begin{align*}
		 m \left( \frac{1}{N} + \Lambda_\tau \right)  &= c \frac{\sigma}{N} + d \frac{1}{N} + \Lambda_\sigma \\
		 &=  \frac{1}{N} + \Lambda_\sigma
	.\end{align*}
	From this we see that $c \equiv 0, d \equiv 1 \mod N$. 
	\begin{align*}
		m(\frac{\tau}{N} + \Lambda_\tau) &= \frac{m\tau}{N} + \Lambda_\sigma \\
		&= a \frac{\sigma}{N} + b \frac{1}{N} + \Lambda_\sigma \\
		&= \frac{\sigma}{N} \\
	.\end{align*}
	So $a \equiv 1, b \equiv 0 \mod N$
	It follows that $\gamma  \in \Gamma(N)$.

	\rtl Suppose that $\tau = \gamma \cdot \sigma$ for some \[
		\gamma = \begin{pmatrix} a & b \\ c & d  \end{pmatrix} \in \Gamma_1(N)
	.\] 	
	Define $m = c \sigma + d$. Reversing the argument for the other implication yields that $\phi:z \mapsto m z$ is an isomorphism.
	\end{enumerate}
\end{proof}

\subsection{Reintepreting Modular Forms} \label{sec:reintepreting_modular_forms}

@@

The Weierstrass function $\wp_{\Lambda}$ has only one pole of order 2. Hence in this case  $n = 2$.
\item 
	We will show this by first calculating \[
		\frac{1}{2\pi i}\int_{\partial P + t} z \frac{f(z)'}{f(z)} \mathrm d z
	\]
	and showing that this value must be in $\Lambda$.
	Like in the first part of this exercise we will split up the boundary in its edges.
	\[	
		\int_{\partial P+ t} z \frac{f'(z)}{f(z)} \mathrm d z = \left(\int_t^{\omega_2 + t} + \int_{\omega_2+t}^{\omega_1 + \omega_2 + t} + \int_{\omega_1 + \omega_2 + t} ^{\omega_1 + t} + \int_{\omega_1}^{t}\right) z \frac{f'(z)}{f(z)} \mathrm dz
	.\]
	By $\Lambda$-periodicity we know that the factor $f'(z) / f(z)$ is the same on opposing edges. Hence we can write \begin{align*}
		\int_{\partial P + t} z \frac{f'(z)}{f(z)} \mathrm d z &= \int_t^{\omega_1 + t} (z + \omega_2 - z) \frac{f'(z)}{f(z)} \mathrm d z + \int_{t}^{\omega_2 + t} (z - z - \omega_1) \frac{f'(z)}{f(z)} \mathrm d z\\
								       &= \omega_2 \int_t^{\omega_1 + t} 1 \; \mathrm d \ln f(z) - \omega_1 \int_t^{\omega_2 +t} 1 \; \mathrm d \ln f(z) \\
	.\end{align*} 
	From this we see that the integrals must be integer multiples of  $2\pi i$. 
	Hence 
	\[
		\frac{1}{2\pi i } \int_{\partial P + t} z \frac{f'(z)}{f(z)} \mathrm d z \in \Lambda
	.\] 
	Now note that we can write $f(z) = \sum_{x \in \{\text{poles or zero}\} }(z - x)^{\nu_x(f)}g(z)$ for some some simple function $g$. 
	So \[
		\frac{zf'(z)}{f(z)} = \sum_{x \in \{\text{poles or zero}\} }\nu_x(f) \frac{z}{ z - x} + z \frac{g'(z)}{g(z)}
	.\] 
	Note that this function has poles with residue $x \nu_x(f)$ for every $x$ which is a pole or zero of  $f$. By the residue theorem  \[
		\frac{1}{2\pi i} \int_{\partial P + t} z \frac{f'(z)}{f(z)} \mathrm d z = \sum_{x \in \C / \Lambda} \nu_x(f)  x \in \Lambda 
	.\]  
\end{enumerate}
\end{proof}
\printbibliography
\end{document}
